Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-08 emsoft-2019/Error_Analysis.tex
minor updates

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions. Moveover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions. Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

>>>>

The system has to be robust against a mistake in choosing controller $i$ instead of $j$ (or vice-versa), only when \qstatevarmath falls into the \texttt{tube} between $i$ and $j$, and not for all the points in the two regions. Moreover, we are interested in the worst case scenario where is maximized the difference between the activation functions of any two neighbor regions. Assuming that all points in region $i$ might be erroneously assigned to region $j$, without any  knowledge of the actual value of error \texttt{err}, is a too wide over-approximation of the existing instability.

### 2019-04-08 emsoft-2019/Motiv.tex
minor updates

In this section, we use a classical control example to explain the motivation behind this work. Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account. The linearized continuous-time description for the open-loop system's dynamics is as follows:

@@

	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power. Computing the optimal control input can be efficiently done using for example binary tree search. However, the memory limit is more cruicial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.

>>>>

In this section, we use a classical control example to explain the motivation behind this work. Consider the problem of designing stablizing control for an inverted pendulum which takes (polytopic) constraints over state variables and control inputs into account. The linearized descrete-time description for the open-loop system's dynamics is as follows:

@@

	In practice, EMPC will be implemented over relatively low-price embedded systems which have limited memory capacity and computational power. Computing the optimal control input can be efficiently done using for example binary tree search. However, the memory limit is more crucial as it increases proportional to the number of partitions.	Therefore, we would like to explore ways to reduce required memory for saving different coefficients corresponding to the controllers.

### 2019-04-08 emsoft-2019/RMPC_Daisy.tex
minor updates

\section{Robust MPC and Finite Precision}
\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider class of discrete time linreat time invariant systems
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k
\end{equation}
where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable. Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
\begin{align}
\label{eq:RMPC_prob}
\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
&x_{i+1}=Ax_i+Bu_i\nonumber\\
&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
\end{align}
where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon. By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polydedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytob determined by  a set of linear inequalities $H_ix\leq K_i$. To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}
Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong. Several algorithms are proposed to solve for this problem [references?]. The simplest technique to verify which region \statevarmath belongs to is to make a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

@@

A main issue with implimentation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller. However, these embudded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.

>>>>

\section{Robust MPC and Finite Precision}
\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider class of discrete time linear time invariant systems
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k
\end{equation}
where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable. Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
\begin{align}
\label{eq:RMPC_prob}
\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
&x_{i+1}=Ax_i+Bu_i\nonumber\\
&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
\end{align}
where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon. By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytop determined by  a set of linear inequalities $H_ix\leq K_i$. To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}
Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong. Several algorithms are proposed to solve for this problem [references?]. The simplest technique to verify which region \statevarmath belongs to is to make a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

@@

A main issue with implementation of explicit MPC is that all the products of off-line optimization, including regions' boundaries ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s), have to be stored on the micro-controller. However, these embedded systems have limited memory, in the order of KBs and hence, it is of our interest to minimize the occupied memory.
